---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WorldClimData

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of WorldClimData is to present a faster way to download [WorldClim](https://www.worldclim.org/) data using [piggyback](https://docs.ropensci.org/piggyback/index.html)

## Installation

You can install the development version of WorldClimData from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("brunomioto/WorldClimData")
```

## Data

Currently WorldClimData doesn't have all WorldClim data.

There is only data for the **current** period and the following resolution:

- 10' resolution: All the variables ("bio","elev","prec","srad","tavg","tmax","tmin","vapr","wind")

- 5' resolution: All the variables ("bio","elev","prec","srad","tavg","tmax","tmin","vapr","wind")

- 2.5' resolution: All the variables ("bio","elev","prec","srad","tavg","tmax","tmin","vapr","wind")

- 30" resolution: "elev", "wind"

## Example

The `download_worldclim` function will download the zipped worldclim data into a **WorldClim_data** folder and the unzipped .tiff files into a **WorldClim_data_unzipped** folder inside the working directory.

The folder name can be specified within the function using the `folder_path` argument.

```{r, echo=FALSE, message=FALSE}
devtools::load_all()
```

```{r, eval=FALSE}
library(WorldClimData)
```

```{r example}
download_worldclim(period = "current",
                   variable = "elev",
                   resolution = 10,
                   folder_path = "./WorldClim_data")

```

The above example creates 2 folders (WorldClim_data and WorldClim_data_unzipped) and downloads data for the **Elevation** variable for the **Current** period with a **10'** resolution.
The folder structure is presented below.

```{r, eval=FALSE}
Working directory
├── WorldClim_data
│   └── worldclim_base_v21_current_elev_10m.zip
└── WorldClim_data_unzipped
    └── wc2.1_10m_elev.tif
```

