---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WorldClimData

<!-- badges: start -->
<!-- badges: end -->

The goal of WorldClimData is to present a faster way to download WorldClim data

## Installation

You can install the development version of WorldClimData from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("brunomioto/WorldClimData")
```

## Example

The function `download_worldclim` will download worldclim zipped data to a **WorldClim_data** folder and the unzipped .tiff files to a **WorldClim_data_unzipped** folder inside the working directory.

```{r, echo=FALSE, message=FALSE}
devtools::load_all()
```

```{r, eval=FALSE}
library(WorldClimData)
```

```{r example}
download_worldclim(variable = "elev",
                   resolution = 10)

```
